---
title: "Intro to NLP coding"
author: "Matt Williamson"
date: "2023-02-28"
output: html_document
---
# Loading the libraries

One of the benefits of using `R` is the fact that there is an active community of software developers designing functions to complete all kinds of tasks. Once they've got a set of functions that go well together, they'll package them up into a `library` and that library undergoes a bunch of testing to make sure that everything works properly and that there aren't any risks to users. In order for you to use these packages you first have to call the function that installs them (`install.packages("yourpackagename")`). Once you have the packages installed, you have to load them into your `R` session by calling the `library(yourpackagename)` function (pay attention to the different use of quotes here). We'll do that first so that we have everything we need for the workflow.

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) #this is actually a whole set of packages designed to different data manipulation tasks. We rely on the dplyr package alot for organizing data and the stringr package for dealing with text
library(httr) # for accessing the html from the link
library(tidytext) # for creating a tidy dataframe from the website text data
library(wordcloud) # package for creating word clouds
#library(reshape2) # package to restructure and aggregate data
library(tm) # package for topic modeling
library(topicmodels)# package for topic modeling
library(SnowballC)
library(googledrive)
options(
  gargle_oauth_cache = ".secrets",
  gargle_oauth_email = TRUE
)
```

# Reading the data

Before you can actually do anything with our coding data, we need to get it into your `R` **environment**. We'll use the `read.csv()` function to bring in the most recent version of the spreadheet (you'll have to make sure that the name matches whatever you used), and assign it to an object called `article_codes`. Once you've run this, you should see an object called `article_codes` in your **Environment** pane under the **Data** section. You'll see a summary that says the object has 121 observations of 23 variables. As we code more articles, the number of observations should change, but (in general) we aren't adding any more columns. If you see that there are more than 23 variables, you'll want to make sure that things read in correctly.

```{r read}
# read in the csv with the urls for the articles
folder_url <- "https://drive.google.com/drive/u/0/folders/1ob5sagTtT3svhc7ZKeemd9TiAq1_MsCL"
folder <- drive_get(as_id(folder_url))

gdrive_files <- drive_ls(folder)
id <- gdrive_files[gdrive_files$name == "Article Coding", ]$id
drive_download(id, path = "data/article_coding.csv", overwrite = TRUE)

article_codes <- read.csv(file = 'data/article_coding.csv')
```

# Downloading the articles

In order to do any natural language processing (NLP), we need to get the actual articles and assign them to a data object in our **Environment**. To do that, we need to clean up the data a little. We remove any of the entries that don't have a link to the article (`filter(!Link=='')` keeps all of the rows where `Link` is not blank). Then we add an `id` column to keep track of which article belongs to each row of our coding dataset (`mutate( id=row_number())` mutates the dataset by creating a new column called `id` and giving it the value that the `row_number()` function returns). Once we have the data cleaned, we need to create a vector of all of the links. We'll do that and assign it to an object called `urls`.

```{r cleancodes}
article_codes <- article_codes %>% 
  filter(!Link=='') %>% 
  mutate(id = row_number())

# create a vector or list of the urls from the csv
urls <- article_codes$Link
```

## Looping through the links
**Note that you shouldn't have to change anything here, this section is just to help you know what is happening**

In order to download and store all of the text, we need to create a container to hold them. We do that by creating an empty data frame called `df_article`. We then use a loop (the `for` and `next` parts) to download each article and store it in the `df_article` object. We then change set the column name for the text to `article.text` and create an `id` column.

```{r downloadarticles}
df_article <- data.frame()

### IMPORTANT!!! Must be connected to VPN or on campus for this to work! ###

for (url in urls){ # this was working, but now I am getting an error: Error in content(page, as = "text"): unused argument ("text")
  if(url == "") next
  link <- url
  #if(link == "") next
  page <- GET(link)
  page_text <- httr::content(page, as = 'text')
  text_body <- str_extract_all(page_text, regex("(?<=<p>).+(?=</p>)"), simplify = TRUE) 
  text <- text_body[[2]]
  df_article <- rbind(df_article, text)
}

# Rename and reorder the data frame columns
colnames(df_article) <- c("article.text")
df_article <- df_article %>% mutate(id = row_number()) %>% select(id, article.text)

```

Now that we have the articles and our coding sheet, we can join the two together so that we can start using the data! The `full_join` function keeps only the rows with matches in both datasets. 

```{r joindata}
# from the article_codes data frame select one or more variables/columns you would like to join to df_article
# you can update the columns in select() to include whatever information you'd like
# for example, article type, newspaper, etc. But you need the "id" column so that you can "join" the 2 data frames
df_to_join <- article_codes %>% select(id, Species) 
df_article <- df_article %>% full_join(df_to_join, by = "id")
```

# Cleaning up the text

Before we can make much sense of the data, we need to clean things up a bit by removing punctuation, making everything lower-case, and getting rid of words that are so common they overwhelm the actual subject of the articles. The `unnest_tokens` function deals with punctuation and capitalization. The `stop words` dataset is a pre-made set of common words that need to be removed from most articles before we can proceed with language processing. We might decide that we need to remove some additional words beyond the typical ones. We do that by creating the `my_stop_words` object. Finally, we use the `anti_join` function to get rid of all of the words in our corpus that match the words in our stop words object. `anti_join` takes all of the pieces of the first object *NOT* in the second object. Finally, we might "stem" words to get rid of differences in prefixes or suffixes. This helps us avoid treating words like bear and bears as different terms. We use the `wordStem` function to accomplish this.

```{r txtcln}
# Make a tidy data frame by "unnesting" the tokens
# This automatically removes punctuation and will lowercase all words
tidy_df <- df_article %>% unnest_tokens(word, article.text)

# Remove "stop words" using the SMART lexicon 
data("stop_words")
tidy_df <- tidy_df %>%
  anti_join(stop_words)

# Create a small data frame of your own stop words for this project 
# ("br" and "strong" are part of the html formatting which should come out before making tidy df!)
# This needs to be a data frame so that you can use "anti-join()"
# You can add your own words to this list
my_stop_words <- data.frame(c("br", "strong")) 
colnames(my_stop_words) <-("word")

tidy_df <- tidy_df %>%
  anti_join(my_stop_words) %>% 
  mutate(stem = wordStem(word))

```
## Document Term Matrices

```{r speciesfilter}
species <- c("Beavers")
tidy_df_species <- tidy_df %>%
  filter(Species %in% species)

# Create a document term matrix. You will need this for topic modeling
# You will need to create a word count for all of the words in a document
dtm_species <- tidy_df_species %>% 
  count(id, word) %>%
  cast_dtm(id, word, n)

dtm_species_stem <- tidy_df_species %>% 
  count(id, stem) %>%
  cast_dtm(id, stem, n)

tidy_df_species %>%
  count(stem, sort = TRUE) %>%
  slice_max(n, n=20) %>%  # set the number of words to show
  mutate(stem = reorder(stem, n)) %>%
  ggplot(aes(n, stem)) +
  geom_col(fill = "brown") +
  labs(title = paste("20 Most Common Words in Articles About", species), # update the Species
       y = NULL)
```
### Using n-grams

The above analysis relied solely on the occurrence of single words in the text. We might imagine that multiple words occurring together tells us more than just a single word. These groups of words are call _n-grams_ where the _n_ stands for how many words are in a group (i.e., bigrams means 2-word groups). We can run a similar analysis on n-grams here:
```{r ngrams}
df_bigrams <- df_article %>%
  unnest_tokens(bigram, article.text, token = "ngrams", n = 2) %>%
  filter(!is.na(bigram))


# In order to remove the stop words we have to first separate out the two words into word1 and word2
bigrams_separated <- df_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

# Then filter out stopwords and our own stop words for word1 and word2
bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>%
  filter(!word1 %in% my_stop_words$word) %>%
  filter(!word2 %in% my_stop_words$word)%>% 
  mutate(stem1 = wordStem(word1)) %>% # not sure if we want to stem the words for bigrams or not, but would do so here.
  mutate(stem2 = wordStem(word2))

# Then, calculate new bigram counts. This is optional, but good to check. 
bigram_counts <- bigrams_filtered %>% 
#count(word1, word2, sort = TRUE)
  count(stem1, stem2, sort = TRUE)

bigrams_united <- bigrams_filtered %>%
#  unite(bigram, word1, word2, sep = " ") %>% 
  unite(bigram, stem1, stem2, sep = " ")

dtm_bigrams <- bigrams_united %>% 
  count(id, bigram) %>%
  cast_dtm(id, bigram, n)

bigrams_united %>% 
  filter(.,Species == species) %>% 
  count(bigram, sort=TRUE) %>%
  slice_max(n, n=20) %>%  # set the number of words to show
  mutate(bigram = reorder(bigram, n)) %>%
  ggplot(aes(n, bigram)) +
  geom_col(fill = "brown") +
  labs(title = paste("20 Most bigrams in Articles About", species), # update the Species
       y = NULL)
```

## Sentiment Analyses

```{r sentiment}
sent_species <- tidy_df_species %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

# Use the sentiment word counts data frame to make the plot
sent_species %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) + 
  scale_fill_manual(values=c("tan", "brown")) + # change the colors of the bar plot
  geom_col(show.legend = FALSE) + 
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment", 
       y = NULL,
       title = paste("20 Most Common Words in Articles About", species))
ggsave("sentiment_contribution_beavers.png")

tidy_df_species %>%
  inner_join(get_sentiments("bing")) %>%
  count(id, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(sentiment = positive - negative) %>% 
  ggplot(aes(id, sentiment, fill = sentiment)) + 
  geom_col(show.legend = FALSE) + 
  labs(title = paste("Document Sentiment: Articles About", species)) + 
  ylab("Sentiment") + xlab("Document ID")

ggsave("sentiment_documents_beavers.png")

```

## Word Clouds

```{r wordclouds}
d <- tidy_df_species %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  pivot_wider(id_cols = word, names_from = sentiment, values_from = n, values_fill = 0) %>%
  column_to_rownames(var="word") %>% 
  as.matrix() %>% 
  comparison.cloud(colors = c("blue", "green"),
                   max.words = 100, match.colors = TRUE)

#ggsave("sentiment_wordcloud_beavers.png")
```

```{r lda}
dtm_bigrams_species <- bigrams_united %>% 
  filter(Species==species) %>% 
  count(id, bigram) %>%
  cast_dtm(id, bigram, n)

lda_species <- LDA(dtm_species_stem, k = 8, control = list(seed = 1234))
lda_species_bigrams <- LDA(dtm_species_stem, k=8, control = list(seed = 1234))
topics <- tidy(lda_species, matrix = "beta")
topics_bigrams <- tidy(lda_species_bigrams, matrix = "beta")

terms <- topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup() %>%
  # arrange sorts the data
  arrange(topic, -beta) 
terms_bigrams <- topics_bigrams %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>%
  ungroup() %>%
  # arrange sorts the data
  arrange(topic, -beta) 
terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~ topic, scales = "free") + 
  scale_y_reordered() + 
  labs(title = "Term Beta Values for 4 Topics")

terms_bigrams %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~ topic, scales = "free") + 
  scale_y_reordered() + 
  labs(title = "Term Beta Values for 4 Topics")
```